Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-13 ms.tex
Add radial integrand image
More stuff on marginalization

\documentclass{iopart}
\usepackage{amsopn}
\usepackage{iopams}
\usepackage{bib/aas_macros}
\usepackage[colorlinks]{hyperref}
\input{ligo-acronyms/acronyms}

@@

>>>>

\documentclass{iopart}
\usepackage{amsopn}
\usepackage{iopams}
\usepackage{graphicx}
\usepackage{bib/aas_macros}
\usepackage[colorlinks]{hyperref}
\input{ligo-acronyms/acronyms}

@@

The marginalization over $D_\mathrm{L}$, $\cos \iota$, and $psi$ must be done numerically. The outermost integration is over $\cos \iota$ and $\psi$, and is done with Newton-Cotes by evaluating $\mathcal{L}_\mathrm{SNR}$ on a regular lattice in $\cos \iota$ and $\psi$. This integration scheme is first order in $\cos \iota$ and second order in $\psi$.

The innermost integration is over $D_\mathrm{L}$ and is performed using adaptive Gaussian quadrature, but with a twist that speeds up convergence.

\begin{figure}
    \caption{\label{fig:radial_integrand}Illustration of initial subdivisions for radial integration scheme.}
    \begin{center}
        \includegraphics{radial_integrand}
    \end{center}
\end{figure}
